---
title: "Data Visualization"
date: "`r Sys.Date()`"
output: html_document
text.align: justify
---

----

#### Task 1: Download and load the required packages:

```{r}
#loading the ggplot2 and readr packages
library(ggplot2)
library(readr)
```

----

#### Task 2: Load, view and return the structure of the mtcars

```{r}
data(mtcars) #loading the mtcars data set 
View(mtcars) #Viewing the mtcars data set 
str(mtcars)  # returning the structure of the mtcars 
```

----

#### Task 3: Follow the instructions sheet.
```{r}
#adding a histogram 
#using the mtcars dataset 
#adjusting the width of bins to 4
#changing the border color to white and the fill color to red and the bins to 4 using the geom_histogram
#adding x and y axis labels, adding the title and the subtitle
ggplot(data=mtcars, aes(x=mpg)) + geom_histogram(color="white", fill="red", bins=4) +labs(x="Mile per Gallon (mpg)", y="Count", title=" A Histogram for MPG
", subtitle=" mtcars dataset") + theme_bw()
```

----

#### Task 4: Follow the instructions sheet.

```{r}
#Adding a histrogram with border color blue and the binwidth to 3
#Using labs to add x and y label's 
#Using fill=factor(cyl) to change the color of histogram 
#Using facet_wrap(~cyl) to make 3 seperate graphs
#Moving the legend position on the top using (legend.position="top")
ggplot(data=mtcars, aes(x=carb, fill=factor(cyl))) + geom_histogram(color="blue", binwidth=3) + labs(x="Carburetors", y="Frequency") + theme_light() + facet_wrap(~cyl) + theme(legend.position="top")
ggsave("Facetted histogram.png")
```

----

#### Task 5: Follow the instructions sheet.

```{r}
#Adding a geom_bar and changing the width to 0.5
#Using labs to add x, y, and title label's 
#Using fill=factor(cyl) to change the color of barplot  
#Using the legend position to remove the legend 
#Using the factor() method to convert the cyl variable to factor
ggplot(data=mtcars, aes(x=factor(cyl), fill=factor(cyl))) + geom_bar(width=0.5) + labs(x="Cylinder", y="Count", title="Bar plot for mtcars cylinders") + theme_bw() + theme(legend.position="remove")
ggsave("mtcars cylinders.png")
```

----

#### Task 6: Download the Train_crash dataset and set the workdirectory.

```{r}
# Download the Train_crash dataset.
# Set the working directory where you saved the Train_crash dataset.
```

----

#### Task 7: Load, view and return the structure of the Train_ds dataset.

```{r}
#Loading the Train_crash.csv ans assigning it to variable called Train_ds.
Train_ds<-read.csv("Train_crash.csv")
View(Train_ds) #Viewing the Train_ds dataset
str(Train_ds)  #Returning the structure of  Train_ds dataset
```

----

#### Task 8: Add a bar plot showing the Survival Rate.

```{r}
#Adding X, Y, and title using the labs method 
#Using the factor() method to convert the Survived variable to factor
#using fill=factor() too get 2 different bars
#changing the theme to theme_light()
#Using geom_bar to change the width to 0.5
ggplot(data=Train_ds, aes(x=factor(Survived), fill=factor(Survived))) + geom_bar(width=0.5) + labs(x="Survived", y="Passenger Count", title="Train Crash Survival Rate") + theme_light()
```

----

#### Task 9: Add a bar plot showing the Survival Rate by gender.

```{r}
#Adding X, Y, and title using the labs method 
#Using the factor() method to convert the Survived variable to factor
#using fill=factor() too get multi color bars 
#changing the theme to theme_bw()
#Using geom_bar to change the width to 0.5
ggplot(data=Train_ds, aes(x=factor(Survived), fill=factor(Gender))) + geom_bar(width=0.5) + labs(x="Survived", y="Passenger Count", title="Train Crash Survival Rate by Gender") + theme_bw()
```

----

#### Task 10: Add a bar plot showing the Ticket Class by Gender

```{r}
#Adding X, Y, and title using the labs method 
#Using the factor() method to convert the Tick_Class variable to factor
#using fill=factor() too get 2 different color bars
#changing the theme to theme_bw()
#Using position="dodge" to make the bar side by side 
#Using geom_bar to change the width to 0.8
ggplot(data=Train_ds, aes(x=factor(Tick_Class), fill=factor(Gender))) + geom_bar(width=0.8, position="dodge") + labs(x="Ticket Class", y="Passenger Count", title="Ticket Class by Gender") + theme_bw()
```


----

#### Task 11: Add a bar plot showing the Survival Rate by Ticket Class

```{r}
#Adding X, Y, and title using the labs method 
#Using the factor() method to convert the Tick_Class variable to factor
#using fill=factor() too get 2 different color bars
#changing the theme to theme_light()
#Using position="dodge" to make the bar side by side 
#Using geom_bar to change the width to 0.7
ggplot(data=Train_ds, aes(x=factor(Tick_Class), fill=factor(Survived))) + geom_bar(width=0.7, position="dodge") + labs(x="Ticket Class", y="Passenger Count", title="Train Crash Survival Rates by Ticket Class") + theme_light()
```

----

#### Task 12: Add a bar plot showing the Ticket Class per the Embarked Port

```{r}
#Adding X, Y, and title using the labs method 
#Using the factor() method to convert the Tick_Class variable to factor
#using fill=factor() too get 3 different color bars
#changing the theme to theme_light()
#Using position="dodge" to make the bar side by side 
#Using geom_bar to change the width to 0.8
ggplot(data=Train_ds, aes(x=factor(Tick_Class), fill=factor(Port_embark))) + geom_bar(width=0.8, position="dodge") + labs(x="Ticket Class", y="Passenger Count", title=" Ticket Class per the Embarked Port") + theme_light()
```

----

#### Task 13: Add a bar plot showing the Embarked Port Survival Rate by Ticket Class

```{r}
#Adding X, Y, and title using the labs method 
#Using the factor() method to convert the Survived variable to factor
#using fill=factor() too get 3 different color bars
#changing the theme to theme_light()
#Using position="dodge" to make the bar side by side 
#Using geom_bar to change the width to 0.8
#Using facet_wrap() to make 3 different graphs 
ggplot(data=Train_ds, aes(x=factor(Survived), fill=factor(Tick_Class))) + geom_bar(width=0.8, position="dodge") + labs(x="Survived", y="Passenger Count", title="Embarked Port Survival Rate by Ticket Class") + theme_light() + facet_wrap(~Port_embark)

```

----

#### Task 14: Add a bar plot showing the Gender Survival Rate by Ticket Class

```{r}
#Adding X, Y, and title using the labs method 
#Using the factor() method to convert the Tick_Class variable to factor
#using fill=factor() too get 2 different color bars
#changing the theme to theme_light()
#Using position="dodge" to make the bar side by side 
#Using geom_bar to change the width to 0.7
#Using facet_wrap() to make 2 different graphs 
ggplot(data=Train_ds, aes(x=factor(Survived), fill=factor(Tick_Class))) + geom_bar(width=0.7, position="dodge") + labs(x="Survived", y="Passenger Count", title="Gender Survival Rate by Ticket Class") + theme_light() + facet_wrap(~Gender)
ggsave("Gender Survival Rate by Ticket Class.png")
```

----
